Reanalysis Step 5: Main Effects Outcome Analysis

### 2025-08-31 reanalysis-5-outcome_analysis.qmd
fix contrasts

    # Calculate AME with clustering and weights
    # marginaleffects handles survey designs well
    ame <- avg_slopes(
      fitted_models[[i]], 
      variables = "ever_lapse_binary1",
      newdata = imp_data,
      vcov = ~e_mrn_deidentified,  # Cluster SEs on patient ID
      wts = imp_data$weights  # Apply PS weights
    )

>>>>

    # Calculate AME with clustering and weights
    # marginaleffects handles survey designs well
    # the model already handled the clustering
    ame <- marginaleffects::avg_comparisons(
      model,
      variables = "ever_lapse_binary",
      type = "response"   # average difference in predicted probabilities
    )
